mixchar

### 2018-08-18 README.Rmd
devel version. add cran install to readme

[![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
[![codecov](https://codecov.io/gh/smwindecker/mixchar/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/mixchar)
[![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)

@@

You can install `mixchar` from [GitHub](https://github.com/) with:

>>>>

[![CRAN](http://www.r-pkg.org/badges/version/mixchar)
[![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
[![codecov](https://codecov.io/gh/smwindecker/mixchar/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/mixchar)
[![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)

@@

You can install `mixchar` by:

```{r, eval = FALSE}
install.packages("mixchar")
```

or install the development version from [GitHub](https://github.com/) with:
